Enter our title here

### 2017-08-14 manuscript.tex
added gamification section draft

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition 
to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an 
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own 
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}. 
*Swirl can be linked to a Coursera gradebook- learners can have swirl automatically notify coursera of a completed lesson
but this is not avaiblable for the classroom setting (coursera website) so should I include this?*

@@

Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality 
\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so any object defined in a previous exercise needs to be 
defined again.

>>>>

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition 
to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an 
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own 
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.

*Swirl can be linked to a Coursera gradebook- learners can have swirl automatically notify coursera of a completed lesson
but this is not avaiblable for the classroom setting (coursera website) so should I include this?*

@@

Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality 
\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so any object defined in a previous exercise needs to be 
defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. If the student completes the exercise without 
any help they will recieve the full points. If they ask for a hint, 30 percent of the available points will be deducted and 
all of the points will be deducted if they ask for the entire answer. When in a classroom group, students can view their 
progress (points and chapters completed) as well as then progress of their peers. This can help students perform better 
because they want to be on par with the rest of the class; furthermore, when students can see the number of available points 
for an exercise it will motivate them to meet their personal achievement goals. \citep{Chang2016}.
